From noise to knowledge: how randomness generates novel phenomena and information

### 2017-10-21 appendix/appendix.Rmd
rename

```{r}
library(nimble)
library(tidyverse)
```

@@

p <- 
  data.frame(
  data.frame(r = .1, K = 5,  b = .1, c = .1, d = .1, N = 500),
  data.frame(sigma_x = c(.00001,0.01),  sigma_y = c(.00001,0.01)))

@@

quasicycle_df %>%
  gather(species, pop, -t, -sigma) %>%
  ggplot(aes(t, pop, col=species)) + geom_line() + facet_wrap(~sigma)
```

>>>>

```{r}
library(nimble)
library(hrbrthemes)
library(tidyverse)
ggplot2::theme_set(hrbrthemes::theme_ipsum())
```

@@

p <- 
  data.frame(
  data.frame(r = .1, K = 5,  b = .1, c = .1, d = .1, N = 800),
  data.frame(sigma_x = c(.00001,0.01),  sigma_y = c(.00001,0.01)))

@@

read_csv("quasicycles.csv") %>%
  gather(species, pop, -t, -sigma) %>%
  ggplot(aes(t, pop, col=species)) + geom_line() + facet_wrap(~sigma) + scale_color_ipsum()
```

### 2017-10-21 paper.Rmd
rename

@@

@@

@@

- Measuring stability
- Early warning signals
- maximum entropy methods

>>>>

```{r include=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(hrbrthemes)
library(tidyverse)
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```

@@

Stochasticity is most often thought of as something which obscures patterns we are trying to infer.  This is a simple consequence of modeling: as discussed above, variables of interest to the processes in question are modeled explicitly (e.g. change in population density as it depends on the current density), while anything else known to also impact

<!-- blah blah fixed effects vs random effects -->

@@

Understanding the origin of sustained oscillations has long been a central question in ecology [@Hastings1996].  The simple Lotka Volterra model produces only neutrally stable centers, while the more realistic model that introduces carrying capacity for prey as they compete for resources results in a model that produces only damped oscillations, eventually settling into a stable state (Figure 1a).

```{r}
read_csv("appendix/quasicycles.csv") %>%
  gather(species, pop, -t, -sigma) %>%
  ggplot(aes(t, pop, col=species)) + geom_line() + 
  facet_wrap(~sigma) + scale_color_ipsum() + 
  labs(x="Time", 
       y="Population density",
       title="Quasi-cycles created by stochastic resonance",
       subtitle="Left panel: neglible  noise results only in damped oscillations.
                 Right panel: small noise creates sustained oscillations.")
```

@@

- Measuring stability
- Early warning signals
